Model Finding for Recursive Functions in SMT\thanks{ This research is partially supported by the Inria technological development action ``Contre-exemples Utilisables par Isabelle et Coq'' (CUIC). }

### 2015-05-05 tex/main.tex
work on tables

\begin{figure}[t]
\noindent\hbox{}{\hfill
\begin{tabular}{l@{\kern0.5em}rr@{\kern0.5em}rr@{\kern0.5em}rr@{\kern0.5em}rr}
  & \multicolumn{2}{c@{\kern0.5em}}{{\bench z3}}     & \multicolumn{2}{c@{\kern0.5em}}{{\bench cvc4}}     & \multicolumn{2}{c@{\kern0.5em}}{{\bench cvc4+f}}     & \multicolumn{2}{c@{\kern0.5em}}{{\bench cvc4+i}}
\\[-.25\jot]
  & \multicolumn{1}{c}{u} & s
  & u & s
  & u & s
  & u & s
\\
\midrule
{\bench isa} & 14  & 0 & 15  & 0 & 15  & 0 & {\win 61}  & 0
\\
{\bench leon}  & 73  & 0 & 80  & 0 & 80  & 0 & {\win 96}  & 0
\\
{\bench isa+m} & 17  & 0 & 18  & 0 & 18  & 0 & {\win 44}  & 0
\\
{\bench leon+m}  & 83  & 11  & 103 & 6 & 104 & 6 & {\win 117} & 6
\\
Total & 187 & 11  & 216 & 6 & 217 & 6 & {\win 318} & 6
\end{tabular}\hfill\hfill
\begin{tabular}{l@{\kern0.5em}rr@{\kern0.5em}rr@{\kern0.5em}rr@{\kern0.5em}rr}
  & \multicolumn{2}{c@{\kern0.5em}}{{\bench z3}}     & \multicolumn{2}{c@{\kern0.5em}}{{\bench cvc4}}     & \multicolumn{2}{c@{\kern0.5em}}{{\bench cvc4+f}}     & \multicolumn{2}{c@{\kern0.5em}}{{\bench cvc4+i}}
\\[-.25\jot]
  & u & s & u & s & u & s & u & s
\\
\midrule
{\bench isa+w} & 15  & 0 & 15  & 0 & 15  & 0 & 14  & 0
\\
{\bench leon+w}  & 78  & 2 & 80  & 0 & 76  & {\win 9} & 78  & 0
\\
{\bench isa+mw}  & 18  & 35  & 18  & 0 & 18  & {\win 153} & 17  & 0
\\
{\bench leon+mw} & 98  & 75  & 98  & 6 & 95  & {\win 169} & 98  & 6
\\
Total & 209 & 112 & 211 & 6 & 204 & {\win 331} & 207 & 6
\end{tabular}\hfill\hbox{}

}
\caption{\,Number of unsat (u) and sat (s) responses for of all configurations on benchmarks
before and after the translation $\conv$}
\label{fig:results}
\end{figure}

>>>>

\begin{figure}[t]
\normalsize
\centering
\begin{tabular}{l@{\kern1.5em}r@{\kern0.375em}r@{\kern1.5em}r@{\kern0.375em}r@{\kern1.5em}r@{\kern0.375em}r@{\kern1.5em}r@{\kern0.375em}r}
  & \multicolumn{2}{c@{\kern1.5em}}{{\bench z3}}     & \multicolumn{2}{c@{\kern1.5em}}{{\bench cvc4}}     & \multicolumn{2}{c@{\kern1.5em}}{{\bench cvc4+f}}     & \multicolumn{2}{c@{\kern1.5em}}{{\bench cvc4+i}}
\\[-.25\jot]
  & \hfill u \hfill & \hfill s \hfill
  & \hfill u \hfill & \hfill s \hfill
  & \hfill u \hfill & \hfill s \hfill
  & \hfill u \hfill & \hfill s \hfill
\\
\midrule
{\bench isa} & 14  & 0 & 15  & 0 & 15  & 0 & {\win 61}  & 0
\\
{\bench leon}  & 73  & 0 & 80  & 0 & 80  & 0 & {\win 96}  & 0
\\
{\bench isa+m} & 17  & 0 & 18  & 0 & 18  & 0 & {\win 44}  & 0
\\
{\bench leon+m\phantom{w}}  & 83  & {\win 11}  & 103 & 6 & 104 & 6 & {\win 117} & 6
\\[\jot]
Total & 187 & {\win \phantom{0}11}  & 216 & \phantom{00}6 & 217 & \phantom{00}6 & {\win 318} & \phantom{00}6
\end{tabular}
\caption{\,Number of unsat (u) and sat (s) responses on original benchmarks}
\label{fig:results}
\end{figure}

\begin{figure}[t]
\normalsize
{
\centering
\begin{tabular}{l@{\kern1.5em}r@{\kern0.375em}r@{\kern1.5em}r@{\kern0.375em}r@{\kern1.5em}r@{\kern0.375em}r@{\kern1.5em}r@{\kern0.375em}r}
  & \multicolumn{2}{c@{\kern0.375em}}{{\bench z3}}     & \multicolumn{2}{c@{\kern0.375em}}{{\bench cvc4}}     & \multicolumn{2}{c@{\kern0.375em}}{{\bench cvc4+f}}     & \multicolumn{2}{c@{\kern0.375em}}{{\bench cvc4+i}}
\\[-.25\jot]
  & \hfill u \hfill & \hfill s \hfill
  & \hfill u \hfill & \hfill s \hfill
  & \hfill u \hfill & \hfill s \hfill
  & \hfill u \hfill & \hfill s \hfill
\\
\midrule
{\bench isa+w} & 15  & 0 & 15  & 0 & 15  & 0 & 14  & 0
\\
{\bench leon+w}  & 78  & 2 & 80  & 0 & 76  & {\win 9} & 78  & 0
\\
{\bench isa+mw}  & 18  & 35  & 18  & 0 & 18  & {\win 153} & 17  & 0
\\
{\bench leon+mw} & 98  & 75  & 98  & 6 & 95  & {\win 169} & 98  & 6
\\[\jot]
Total & 209 & 112 & 211 & \phantom{00}6 & 204 & {\win 331} & 207 & \phantom{00}6
\end{tabular}

}
\caption{\,Number of unsat (u) and sat (s) responses on translated benchmarks}
\label{fig:results}
\end{figure}
